Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
fix typo reported by Pierre

Our proof was based on the construction of a battle between Herculus and the hydra where the
number of copies at each round was given by the elimination of an existential quantifier. So, it was mandatory to consider the class of \emph{all} hydra battles, or, equivalently, the class of battles where the hydra choses arbitrarily its number $n$ of copies at every round of the battle.

>>>>

Our proof was based on the construction of a battle between Hercules and the hydra where the
number of copies at each round was given by the elimination of an existential quantifier. So, it was mandatory to consider the class of \emph{all} hydra battles, or, equivalently, the class of battles where the hydra choses arbitrarily its number $n$ of copies at every round of the battle.
